Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-04 rmd/Manuscript.tex
Finally got the redistribution data ready. Will run spatial analyses tomorrow

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-29}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline\textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

@@

\section{Introduction}\label{introduction}

Marine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from extractive activities such as fishing. Current international
goals aim to ``effectively protect 10\% of the ocean environments by
2020''. In an effort to meet this target, the world has seen a rapid
increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
part of this rapid increase can be attributed to the designation of a
small number of Large Scale Marine Protected Areas {[}LSMPAs;
\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
km\textsuperscript{2} \citep{toonen_2013} in extension, and are often
implemented in the pelagic environment, where the dominant human
activity is industrial fishing \citep{gray_2017}.

@@

\section{Methods}\label{methods}

@@

\subsection{Data}\label{data}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods.}
\end{figure}

@@

\subsection{Analysis}\label{analysis}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend_ps}, and the relative temporal change is presented
in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 12 and
n = 10\footnote{This number is likely to change upon finalizing the
  spatial analysis of longliners, which is currently running.} spatially
defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
for purse seiners and longliners, respectively.

@@

\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -11.48 & -8.54\\
KIR & 1.28 & 2.76\\
HS & 0.00 & 0.00\\
COK & 0.00 & 0.34\\
FSM & 0.00 & 0.55\\
\addlinespace
MHL & NA & -0.55\\
NRU & 0.00 & 0.16\\
PNG & 0.00 & -10.02\\
SLB & -8.48 & 2.13\\
TKL & NA & 0.19\\
\addlinespace
TUV & 7.23 & 1.47\\
others & 22.55 & 11.51\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Results}\label{results}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for longliners. \textbf{This are preliminar results, contingent
on the spatial analysis currently being run}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryothers & 0.016 (0.021) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryothers & 0.201$^{***}$ (0.028) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Observations & 864 \\ 
R$^{2}$ & 0.557 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\section{Discusion}\label{discusion}

@@

\section{Appendix}\label{appendix}

>>>>

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-10-03}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline \textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Marine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from extractive activities such as fishing. Current international
goals aim to ``effectively protect 10\% of the ocean environments by
2020''. In an effort to meet this target, the world has seen a rapid
increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
part of this rapid increase can be attributed to the designation of a
small number of Large Scale Marine Protected Areas {[}LSMPAs;
\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
km\textsuperscript{2} in extension \citep{toonen_2013}, and are often
implemented in the pelagic environment, where the dominant human
activity is industrial fishing \citep{gray_2017}.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{data}{%
\subsection{Data}\label{data}}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods.}
\end{figure}

@@

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend_ps}, and the relative temporal change is presented
in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 31 and
n = 33\footnote{This number is likely to change upon finalizing the
  spatial analysis of longliners, which is currently running.} spatially
defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
for purse seiners and longliners, respectively.

@@

\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -6.68 & -8.54\\
KIR & -8.14 & 2.76\\
HS & 13.76 & 11.03\\
ASM & 0.00 & -0.08\\
CHN & 0.02 & 0.01\\
\addlinespace
COK & 0.32 & 0.34\\
ECU & NA & 0.01\\
FJI & 0.02 & 0.01\\
FSM & 0.00 & 0.55\\
GUM & NA & 0.00\\
\addlinespace
JPN & -0.01 & 0.01\\
KOR & 0.00 & 0.00\\
MEX & NA & 0.00\\
MHL & 0.00 & -0.55\\
NIU & NA & 0.00\\
\addlinespace
NRU & 0.00 & 0.16\\
NZL & NA & 0.59\\
PAN & NA & 0.01\\
PHL & NA & 0.00\\
PNG & 0.00 & -10.02\\
\addlinespace
PYF & 0.00 & 0.02\\
SEN & NA & 0.01\\
SLB & -3.00 & 2.13\\
SYC & 0.06 & 0.07\\
TKL & 0.00 & 0.19\\
\addlinespace
TON & 0.00 & 0.01\\
TUV & 2.08 & 1.47\\
TWN & 0.00 & 0.00\\
UMI & 0.05 & -0.20\\
WLF & 0.00 & 0.00\\
\addlinespace
WSM & NA & 0.04\\
ATF & 0.00 & NA\\
CHL & 0.00 & NA\\
COM & 0.00 & NA\\
GHA & 0.00 & NA\\
\addlinespace
MDG & -0.08 & NA\\
MNP & 0.00 & NA\\
MOZ & 1.29 & NA\\
MUS & 0.27 & NA\\
PCN & 0.00 & NA\\
\addlinespace
TZA & 0.04 & NA\\
ZAF & 0.00 & NA\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for longliners. \textbf{This are preliminar results, contingent
on the spatial analysis currently being run}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & 0.003 (0.019) \\ 
  countryASM & $-$0.087$^{***}$ (0.018) \\ 
  countryCHN & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryECU & $-$0.088$^{***}$ (0.018) \\ 
  countryFJI & $-$0.089$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryGUM & $-$0.089$^{***}$ (0.018) \\ 
  countryJPN & $-$0.089$^{***}$ (0.018) \\ 
  countryKOR & $-$0.089$^{***}$ (0.018) \\ 
  countryMEX & $-$0.089$^{***}$ (0.018) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNIU & $-$0.089$^{***}$ (0.018) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryNZL & $-$0.080$^{***}$ (0.019) \\ 
  countryPAN & $-$0.089$^{***}$ (0.018) \\ 
  countryPHL & $-$0.089$^{***}$ (0.018) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countryPYF & $-$0.089$^{***}$ (0.018) \\ 
  countrySEN & $-$0.089$^{***}$ (0.018) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countrySYC & $-$0.089$^{***}$ (0.018) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTON & $-$0.089$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryTWN & $-$0.089$^{***}$ (0.018) \\ 
  countryUMI & $-$0.086$^{***}$ (0.018) \\ 
  countryWLF & $-$0.089$^{***}$ (0.018) \\ 
  countryWSM & $-$0.089$^{***}$ (0.018) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.196$^{***}$ (0.023) \\ 
  post:countryASM & 0.085$^{***}$ (0.018) \\ 
  post:countryCHN & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryECU & 0.085$^{***}$ (0.018) \\ 
  post:countryFJI & 0.086$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryGUM & 0.085$^{***}$ (0.018) \\ 
  post:countryJPN & 0.085$^{***}$ (0.018) \\ 
  post:countryKOR & 0.085$^{***}$ (0.018) \\ 
  post:countryMEX & 0.085$^{***}$ (0.018) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNIU & 0.085$^{***}$ (0.018) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryNZL & 0.091$^{***}$ (0.019) \\ 
  post:countryPAN & 0.085$^{***}$ (0.018) \\ 
  post:countryPHL & 0.085$^{***}$ (0.018) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countryPYF & 0.086$^{***}$ (0.018) \\ 
  post:countrySEN & 0.085$^{***}$ (0.018) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countrySYC & 0.086$^{***}$ (0.018) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTON & 0.086$^{***}$ (0.018) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryTWN & 0.085$^{***}$ (0.018) \\ 
  post:countryUMI & 0.083$^{***}$ (0.018) \\ 
  post:countryWLF & 0.085$^{***}$ (0.018) \\ 
  post:countryWSM & 0.086$^{***}$ (0.018) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Observations & 2,304 \\ 
R$^{2}$ & 0.638 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\hypertarget{discusion}{%
\section{Discusion}\label{discusion}}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}
